### 2017-02-13 section/3_redundancy.tex
remove red

{\color{red}
We calculate the redundancy for an input instruction $I$ based on the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances
and the lengths of the two sequences, denoted by $SeqA$ and $SeqB$. 
The intuition is that the redundancy rate should be 1 if one sequence is the 
sub-sequence of the other, and be 0 if these two
sequences are completely different.
}
The exact formula is the following:
%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

>>>>

We calculate the redundancy for an input instruction $I$ based on the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances
and the lengths of the two sequences, denoted by $SeqA$ and $SeqB$. 
The intuition is that the redundancy rate should be 1 if one sequence is the 
sub-sequence of the other, and be 0 if these two
sequences are completely different.
The exact formula is the following:
%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

### 2017-02-13 section/5_exper.tex
remove red

{\color{red}
\noindent\textbf{Research questions to answer}
We mainly conduct three sets of evaluation to answer three key research 
questions regarding the coverage, accuracy, and performance of \Tool,

@@

\textbf{RQ3}.
What is the run-time overhead of \Tool? (Sec.\ref{sec:result_perf})
}

\subsection{Coverage Results}
\label{sec:coverage}
{\color{red}
To answer \textbf{RQ1}, we apply \Tool to real root-cause loops to see if 
it can accurately identify inefficiency categories.
As shown by the check-marks in Table~\ref{tab:benchmarks}
(the ``Did \Tool Identify ..?'' columns), 
\Tool does provide good diagnosis coverage.
}
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that match what developers took in practice
for 33 out of \allbugs cases.

@@

%\input section/tab_top5
{\color{red}
To answer \textbf{RQ2}, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all benchmarks
and then apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}.
}
{\color{red}
Table \ref{tab:benchmarks} shows that \Tool is accurate, having five real
false positives and 17 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

@@

\Tool also reports 17 benign false positives. These are 
correctly identified inefficient loops.
However, they are not the main contributors to the perceived
performance problems, and hence are not
fixed in patches. 
Different from the five false positives discussed above, these 17 loops are
ranked {\bf lower} than the true positive loops by statistical debugging, as
well as by profillers,
because of their low contributions to the perceived performance problems.
Consequently, they will not cause extra diagnosis effort for \Tool users.
}

@@

{\color{red}
To answer \textbf{RQ3}, we evaluate the run-time performance of
applying \Tool to the real root-cause loop. 
}
As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla\#347306. 
We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
%the current diagnosis results are obtained by running the
%program only \textbf{once} under the problem-triggering workload.
%If we use sparser sampling, more failure runs will be needed to obtain good
%diagnosis results.

>>>>

\noindent\textbf{Research questions to answer}
We mainly conduct three sets of evaluation to answer three key research 
questions regarding the coverage, accuracy, and performance of \Tool,

@@

\textbf{RQ3}.
What is the run-time overhead of \Tool? (Sec.\ref{sec:result_perf})

\subsection{Coverage Results}
\label{sec:coverage}
To answer \textbf{RQ1}, we apply \Tool to real root-cause loops to see if 
it can accurately identify inefficiency categories.
As shown by the check-marks in Table~\ref{tab:benchmarks}
(the ``Did \Tool Identify ..?'' columns), 
\Tool does provide good diagnosis coverage.
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that match what developers took in practice
for 33 out of \allbugs cases.

@@

%\input section/tab_top5
To answer \textbf{RQ2}, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all benchmarks
and then apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}.
Table \ref{tab:benchmarks} shows that \Tool is accurate, having five real
false positives and 17 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

@@

\Tool also reports 17 benign false positives. These are 
correctly identified inefficient loops.
However, they are not the main contributors to the perceived
performance problems, and hence are not
fixed in patches. 
Different from the five false positives discussed above, these 17 loops are
ranked {\bf lower} than the true positive loops by statistical debugging, as
well as by profillers,
because of their low contributions to the perceived performance problems.
Consequently, they will not cause extra diagnosis effort for \Tool users.

@@

To answer \textbf{RQ3}, we evaluate the run-time performance of
applying \Tool to the real root-cause loop. 
As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla\#347306. 
We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
%the current diagnosis results are obtained by running the
%program only \textbf{once} under the problem-triggering workload.
%If we use sparser sampling, more failure runs will be needed to obtain good
%diagnosis results.

### 2017-02-13 section/evaltax.tex
remove red

Our previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects:
(1) Apache suite, including HTTPD web server written in C/C++,
TomCat server written in Java, and Ant build management tool in Java;
(2) Chromium Google Chrome browser in C/C++;
(3) GCC compiler suite in C/C++;
(4) Mozilla suite, including Firefox web browser and Thunderbird
Email client in C/C++ and JavaScript; 
(5) MySQL database server in C/C++.
{\color{red} By manually inspecting a set of randomly sampled bug reports,
previous work identified 
65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.}  
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study
here.

>>>>

Our previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects:
(1) Apache suite, including HTTPD web server written in C/C++,
TomCat server written in Java, and Ant build management tool in Java;
(2) Chromium Google Chrome browser in C/C++;
(3) GCC compiler suite in C/C++;
(4) Mozilla suite, including Firefox web browser and Thunderbird
Email client in C/C++ and JavaScript; 
(5) MySQL database server in C/C++.
By manually inspecting a set of randomly sampled bug reports,
previous work identified 
65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study
here.
